Refinement of Parallel Algorithms down to LLVM

### 2024-03-23 papers/JAR_SI_ITP2022/main.tex
Diagrams uod

  \begin{figure}
    \plottim{Laptop, uint64}{data_laptop_uint64}{xticklabels={},ytick distance={200}}{\legend{}}
    \plottim{Server, uint64}{data_server_uint64}{xticklabels={},ytick distance={200},ymax=1100}{\legend{}}
    \plottim{Laptop, string}{data_laptop_llstring}{xticklabels={},ytick distance={200},ymax=1100}{\legend{}}
    \plottim{Server, string}{data_server_llstring}{
      xlabel near ticks, x tick label style={rotate=45,anchor=east,font=\tiny},
      ytick distance={200},ymax=1000,
      legend style = {
%         legend pos= north east,
        at = {(.87,.97)},
        cells={anchor=west},
        font=\tiny
      },
    }{}

@@

  \begin{tikzpicture}
    \begin{axis}[
      xlabel near ticks,
      legend style = {
        at = {(.97,.4)},
        cells={anchor=west},
        font=\footnotesize
      },
      ymajorgrids,
      xmin=1, ymin=1, xmax=12, ymax=8,
      title={\large Laptop (u64)},
      title style={at={(0.25,.75)}},
      width=.54\textwidth,
      height=.3\textheight
    ]
      \input{sudata_uint64_laptop}

>>>>

  \begin{figure}
    \plottim{Laptop, uint64}{data_laptop_uint64}{xticklabels={},ytick distance={200}}{\legend{}}
    \plottim{Server, uint64}{data_server_uint64}{xticklabels={},ytick distance={200},ymax=1100}{\legend{}}
    \plottim{Laptop, string}{data_laptop_llstring}{xticklabels={},ytick distance={200},ymax=1100}{\legend{}}
    \plottim{Server, string}{data_server_llstring}{
      xlabel near ticks, x tick label style={rotate=45,anchor=east,font=\tiny},
      ytick distance={200},ymax=1000,
      legend style = {
%         legend pos= north east,
        at = {(.77,.97)},
        cells={anchor=west},
        font=\tiny
      },
    }{}

@@

  \begin{tikzpicture}
    \begin{axis}[
      xlabel near ticks,
      legend style = {
        at = {(.97,.35)},
        cells={anchor=west},
        font=\tiny
      },
      ymajorgrids,
      xmin=1, ymin=1, xmax=12, ymax=8,
      title={\large Laptop (u64)},
      title style={at={(0.25,.75)}},
      width=.54\textwidth,
      height=.3\textheight
    ]
      \input{sudata_uint64_laptop}
